Ensemble Stability of Biological Networks

### 2014-09-26 paper.tex
update references to separated figures

% \section{Cycle number and connectivity classify robust systems}
The combination of connectivity and cycle number as shown in \ref{fig:combined}E provides a better classification of the dependence of robustness upon network topology. Here the robustness of three component systems with a given number of cycles, increases monotonically with connectivity. The network with the highest robustness for three component systems is that of \ref{fig:scc}A. This network is the most hierarchical of all three component systems in the sense that it represents a total ordering of the components of the network and its adjacency matrix also shown in \ref{fig:scc}A has a block triangular structure.

This observation suggested that graph edit distance from \ref{fig:scc}A, hierarchy, might provide a better characterization of system robustness. \ref{fig:combined}D shows system robustness as a function of hierarchy, where the most hierarchical system has a hierarchy of 0. There is a monotonic correlation between the upper bound of robustness and hierarchy. \ref{fig:combined}F shows system robustness as a function of both hierarchy and connectivity. The monotonic correlation between hierarchy and robustness is refined by an underlying correlation between robustness and connectivity analogous to that of \ref{fig:combined}E.

>>>>

% \section{Cycle number and connectivity classify robust systems}
The combination of connectivity and cycle number as shown in \ref{fig:connectcycle3D3x3} provides a better classification of the dependence of robustness upon network topology. Here the robustness of three component systems with a given number of cycles, increases monotonically with connectivity. The network with the highest robustness for three component systems is that of \ref{fig:scc}A. This network is the most hierarchical of all three component systems in the sense that it represents a total ordering of the components of the network and its adjacency matrix also shown in \ref{fig:scc}A has a block triangular structure.

This observation suggested that graph edit distance from \ref{fig:scc}A, hierarchy, might provide a better characterization of system robustness. \ref{fig:combined}D shows system robustness as a function of hierarchy, where the most hierarchical system has a hierarchy of 0. There is a monotonic correlation between the upper bound of robustness and hierarchy. \ref{fig:connectdist3D3x3} shows system robustness as a function of both hierarchy and connectivity. The monotonic correlation between hierarchy and robustness is refined by an underlying correlation between robustness and connectivity analogous to that of \ref{fig:connectcycle3D3x3}.
